Dependent Object Types

### 2012-08-30 doc/candidacy/report.tex
more cautious formulation

Mixing composition is not commutative. When expanding a type to a
record type, a compound type $R_1 \with R_2$ expands to a record type
containing the concatenation of the declarations in $R_1$ and $R_2$,
but if some label is defined in both $R_1$ and $R_2$, the definition
in $R_2$ overrides (and so must be more specific than) the definition
in $R_1$. Though this break of commutativity is justified from an
implementation standpoint, it is awkward from a typing standpoint: in
particular, it means that least upper bounds and greatest lower bounds
do not always exist.

>>>>

Mixing composition is not commutative. When expanding a type to a
record type, a compound type $R_1 \with R_2$ expands to a record type
containing the concatenation of the declarations in $R_1$ and $R_2$,
but if some label is defined in both $R_1$ and $R_2$, the definition
in $R_2$ overrides (and so must be more specific than) the definition
in $R_1$. Though this break of commutativity is justified from an
implementation standpoint, it is awkward from a typing standpoint: in
particular, least upper bounds and greatest lower bounds
do not always exist in Scala.
